---
title: "Machine learning_Assignment_3"
author: "Manasa Chelukala"
date: "3/5/2022"
output:
  pdf_document: default
  html_document: default
---
#Importing the Dataset
```{r}
UniversalBank <- read.csv('C:/Users/HP/Documents/csv file/UniversalBank.csv')
summary(UniversalBank)

```
#calling Libraries
```{r}
library(caret)
library(class)
library(ISLR)
```
#Converting Personal.loan Variable

```{r}
UniversalBank$Personal.Loan = as.factor(UniversalBank$Personal.Loan) 

summary(UniversalBank)
```
#Converting Online Variable
```{r}
UniversalBank$Online = as.factor(UniversalBank$Online) 
summary(UniversalBank)
```
#Converting Creditcard Variable
```{r}
UniversalBank$CreditCard = as.factor(UniversalBank$CreditCard) 
summary(UniversalBank)

```
#Task_A
#Data Partition

```{r}
set.seed(64060)
Train_Index = createDataPartition(UniversalBank$Personal.Loan,p=0.6, list=FALSE) # 60% reserved for Train
Train.df=UniversalBank[Train_Index,]
Validation.df=UniversalBank[-Train_Index,]
```

```{r}
mytable <- xtabs(~ CreditCard+Online+Personal.Loan, data=Train.df)
ftable(mytable)
```

#Task_B:what is the probability that this customer will accept the loan offer? [This is the probability of loan acceptance (Loan = 1) conditional on having a bank credit card (CC = 1) and being an active user of online banking services (Online = 1)]
```{r}
Probability = 59/(479+59)
Probability
```


#Task_C:

#pivot table with  Personal loan as row and credit card as column using training data.
```{r}
table(CreditCard=Train.df$CreditCard, Personal.Loan=Train.df$Personal.Loan)
```
#pivot table with  Personal loan as row and Online as column using training data.
```{r}
table(Online=Train.df$Online, Personal.Loan=Train.df$Personal.Loan)
```
#pivot table for Personal loan
```{r}
table(Personal.Loan=Train.df$Personal.Loan)
```

#Task_D:
#i.P(CC = 1 | Loan = 1)(the proportion of credit card holders among the loan acceptors)
```{r}
Probability_1 = 93/(195+93)
Probability_1
```
#ii.P(Online = 1 | Loan = 1) 
```{r}
Probability_2 = 179/(109+179)
Probability_2
```

#iii.P(Loan = 1) (the proportion of loan acceptors) 
```{r}
Probability_3 = 288/(2712+288)
Probability_3
```

#iv.P(CC = 1 | Loan = 0) 
```{r}
Probability_4 = 788/(1924+788)
Probability_4
```

#v.P(Online = 1 | Loan = 0)
```{r}
Probability_5 = 1631/(1631+1081)
Probability_5
```

#vi.P(Loan = 0)
```{r}
Probability_6 = 2712/(2712+288)
Probability_6
```
#Task_E:
#P(Loan = 1 | CC = 1, Online = 1).
```{r}
naive_Bayes_probability <- (Probability_1*Probability_2*Probability_3) / 
                          ((Probability_1*Probability_2*Probability_3) + 
                             (Probability_4*Probability_5*Probability_6))
naive_Bayes_probability
```
#Task_F:Compare this value with the one obtained from the pivot table in (B).
#Which is a more accurate estimate?
```{r}
#0.1087106 in task-E is very similar to the  0.1096654 in task-B.
#The difference between the exact and naive bayes methods is that
#the exact approach requires the same independent variable classifications to predict, 
#whereas the naive bayes method does not.
```


#Task_G:
# P(Loan = 1 | CC = 1, Online = 1)
#Run naive Bayes on the data. Examine the model output on training data, and find the entry 
#that corresponds to P(Loan = 1 | CC = 1, Online = 1). Compare this to the number you 
#obtained in (E).

```{r}
library(e1071)
```

```{r}
nb.model<-naiveBayes (Personal.Loan~Online+CreditCard, data=Train.df)
To_Predict=data.frame(Online= '1', CreditCard= '1')
predict(nb.model,To_Predict,type='raw')
```
#The task-G value of 0.1087106 and the task-E value of 0.1087106 are identical.
#As a result, the naive bayes produces the same results as the prior approaches.
