---
title: "MachineLearning_Assignment_5"
author: "Manasa Chelukala"
date: "4/7/2022"
output:
  pdf_document: default
  html_document: default
---

```{r}
Cereals <- read.csv("C:/Users/HP/Documents/csv file/Cereals.csv")
Cereals <- na.omit(Cereals)
head(Cereals)
```
#Loading the necessary libraries
```{r}
library(cluster)
library(caret)
library(dendextend)
library(factoextra)

```

#Normalizing the Data
```{r}
Cereals <- Cereals[,4:16]
Cereals <- scale(Cereals,center = TRUE,scale = TRUE)
head(Cereals)
```
##Task-1.Apply hierarchical clustering to the data using Euclidean distance to the normalized measurements. 
#Use Agnes to compare the clustering from single linkage, complete 
#linkage, average linkage, and Ward. Choose the best method.
```{r}
## Euclidean distance to measure the Distance
Euclidean_Dist <- dist(Cereals, method = "euclidean")
# Hierarchical clustering using Complete Linkage
hc1 <- hclust(Euclidean_Dist, method = "complete" )
# Plot the obtained dendrogram
plot(hc1, cex = 0.6, hang = -1)

round(hc1$height, 3)

```

```{r}
# Compute with agnes and with different linkage methods
hc_single <- agnes(Cereals, method = "single")
print(hc_single$ac)
hc_complete <- agnes(Cereals, method = "complete")
print(hc_complete$ac)
hc_average <- agnes(Cereals, method = "average")
print(hc_average$ac)
hc_ward <- agnes(Cereals, method = "ward")
print(hc_ward$ac)
```
#The agglomerative coefficient obtained by Ward's method is the largest. 

#visualizing  the dendrogram
```{r}
hc_Ward <- agnes(Euclidean_Dist, method = "ward")
pltree(hc_Ward, cex = 0.6, hang = -1, main = "Dendrogram of agnes for ward") 
```
##Task-2.How many clusters would you choose?
```{r}
#The largest difference in height can be used to determine the k value, hence K =5 is the best option.
hc_Ward <- hclust(Euclidean_Dist,method = "ward.D2")
clust_comp <- cutree(hc_Ward, k=5)
table(clust_comp)
plot(hc_Ward,cex=0.6)
rect.hclust(hc_Ward, k = 5, border = 2:10,)
Temp <- cbind(as.data.frame(cbind(Cereals,clust_comp)))
#Visualizing the clusters in Scatter plot
fviz_cluster(list(data=Euclidean_Dist, cluster = clust_comp))
```

##Task-3.The elementary public schools would like to choose a set of cereals to include in their
#daily cafeterias. Every day a different cereal is offered, but all cereals should support a
#healthy diet. For this goal, you are requested to find a cluster of “healthy cereals.”
```{r}
Healthy_cereal <- na.omit(read.csv("C:/Users/HP/Documents/csv file/Cereals.csv"))
Healthy_cereal<- cbind(Healthy_cereal,clust_comp)
mean(Healthy_cereal[Healthy_cereal$clust_comp==1,"rating"])
mean(Healthy_cereal[Healthy_cereal$clust_comp==2,"rating"])
mean(Healthy_cereal[Healthy_cereal$clust_comp==3,"rating"])
mean(Healthy_cereal[Healthy_cereal$clust_comp==4,"rating"])
mean(Healthy_cereal[Healthy_cereal$clust_comp==5,"rating"])
```
#It is Clear that Cluster1 has maximum rating i.e.73.84446,hence we'll choose it as an healthy cereal.